\section{Introduction}

Dimensionality Reduction Methods for Visualization.
tSNE~\cite{maaten2008tsne}, UMAP~\cite{mcinnes2018umap}.

Co gang giai thich: scores la stochastic variable.
BO co the giai quyet van de do (cai hinh ve tren bang de giai thich voi ban G.)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}

\subsection{Usage of Pairwise Constraints in Unsupervised Learning}


\subsection{Visualization Quality Metrics}


\subsection{Choosing a Good Perplexity for t-SNE}
Automatic selection of perplexity for t-SNE~\cite{cao2017automatic}.


\subsection{Automatic Parameter Tuning with Bayesian Optimization}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Constraint Preserving Score}


\subsection{Visual Definition of the Pairwise Constraints}

\subsection{Quantify the Pairwise Constraints}

\subsection{Basic characteristics of Constraint Preserving Score}

\par ML with CCA
\par CL with BIC
\par ML+CL with AUC\_RNX


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Constraint-based Score as Target in Bayesian Optimization Approach}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experimental Setup}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

This work is based on two fundamental elements:
(1) The $q_{ij}$-based score built upon a limit number of constraints can distinguish the visualizations prefering local structure and those prefereing global structure.
(2) Bayesian Optimization approach provides a solid foundation to estimate the maximum value of any complex blackbox cost function.
With the appropriate setting, BayOpt fit well with the constraint-based score to solve the problem of parameter tuning.

\par
The violated constraints in our methods correspond to the shortcomming of t-SNE in \cite{wattenberg2016use}.
t-SNE can not preserve the within-cluster distances and between-clusters distances.
[TODO: Add reproduced figures].
The $q_{ij}$-based score can help to understand the defective of the visualization.

\par
Easily generate pairwise constraints from labels.
  Only need small amount of labeled points for each class to generate hundreds of constraints.
  The proposed method only need 200 constraints to work well.

\par
Can replace the auto-generated constraints by the manual constraints of the real user.

\par
The user can interact directly in the loop of Bayesian Optimization method to select the next parameter to discover.


\par
Both the constraint-based score and the BayOpt's internal steps are explainable even for the non-technical users. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Work}
